The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-03-28 Paper.Rmd
working on Discussion more

<!--A para that sets up Shya's extinction risk paper - asks about importance of this effect for real 
species and whether it needs to be incorporated into PVA, and in what cases. If the copula structure of environmental variables changes (is it changing?) what will be the impact on extinction risk? Also, there may be copula structure between vital rates, and it is not accounted for in typical stochastic matrix model based PVA. Does it need to be?-->
Although we have demonstrated that tail dependence between environmental variables
can influence extinction risk, substantial work remains to be done regarding the 
circumstances under which this result holds, and its magnitude in different scenarios. 
First, we used 
a non-density dependent model to examine extinction risk; does tail dependence
in environmental variables still influence extinction risk when density dependence
plays a role? Second, we considered metapopulation extinction risk, but the whole field 
of population viability analysis [@REF-Morris and Doak] stochastic matrix modelling

>>>>

<!--A para that sets up Shya's extinction risk paper - asks about importance of this effect for real 
species and whether it needs to be incorporated into PVA, and in what cases. If the copula structure of environmental variables changes (is it changing?) what will be the impact on extinction risk? Also, there may be copula structure between vital rates, and it is not accounted for in typical stochastic matrix model based PVA. Does it need to be?-->
Although we have demonstrated that tail dependence between environmental variables
can influence extinction risk, substantial work remains to be done regarding the 
circumstances under which this result holds, and its magnitude in different scenarios. 
First, we used 
a non-density dependent model to examine extinction risk; does tail dependence
in environmental variables still influence extinction risk when density dependence
plays a role? Second, we considered metapopulation extinction risk, but the whole field 
of population viability analysis [@REF-Morris and Doak] stochastic matrix modelling 
<!--***DAN: Shya, don't work on this para, I am still working on it-->
